\textbf{Computational Fuzzy Extractors}

### 2013-06-24 CompFuzzExt.tex
Added acknowledgements section

\title{\textbf{Computational Fuzzy Extractors}}
\author{Benjamin Fuller\footnote{Email: {\tt bfuller@cs.bu.edu}.  Work done in part while the author was at MIT Lincoln Laboratory.  The work of Benjamin Fuller is sponsored by the United States Air Force under Air Force Contract FA8721-05-C-0002. Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government.}
~~~~~~~~Xianrui Meng\footnote{Email: {\tt xmeng@cs.bu.edu}.}~~~~~~~~~Leonid Reyzin\footnote{Email: {\tt reyzin@cs.bu.edu}.} \\ Boston University}
%\author{}
\begin{document}
\maketitle

@@

%\textbf{Comparison with \thref{thm:lossless secure extractor log}}
%%\thref{thm:lossless block sketch log} is a direct consequence of \thref{thm:blockLWE} and parameter settings~(discussed in  \secref{ssec:block params}).  
%The weaker entropy source means we are able to extract fewer variables~($n/3$ instead of $n/2$) and that we must work over a slightly larger field.  We could set $\alpha$ larger than $n/3$.  This would yield fewer hardcore dimensions and force us to use a larger field.  To extract enough bits and keep the field size polynomial in $n$, $n-\alpha$ must be at least a constant fraction of $n$.  We consider the setting where the number of fixed errors, hardcore dimensions, and dimensions used for randomness are all $n/3$.
%The parameter $\beta$ does not significantly impact the asymptotic behavior but is important for small values of $n$.

>>>>

\title{\textbf{Computational Fuzzy Extractors}}
\author{Benjamin Fuller\footnote{Email: {\tt bfuller@cs.bu.edu}.  Work done in part while the author was at MIT Lincoln Laboratory.}
~~~~~~~~Xianrui Meng\footnote{Email: {\tt xmeng@cs.bu.edu}.}~~~~~~~~~Leonid Reyzin\footnote{Email: {\tt reyzin@cs.bu.edu}.} \\ Boston University}
%\author{}
\begin{document}
\maketitle

@@

\section*{Acknowledgements}
The authors are grateful to Ran Canetti, Yevgeniy Dodis, Nico D\"{o}ttling, Danielle Micciancio, J\"{o}rn M\"{u}ller-Quade, Christopher Peikert, Oded Regev, Adam Smith, and Daniel Wichs for helpful discussions, creative ideas, and important references.  In particular, the authors thank Nico D\"{o}ttling for describing his result on LWE with uniform errors.  The work of Benjamin Fuller is sponsored by the United States Air Force under Air Force Contract FA8721-05-C-0002. Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government.
